Deep Learning Project

### 2024-09-28 project/paper.tex
Update model evaluation and training details in paper
Revised the accuracy metrics for the simple model and added detailed evaluation results for both ImageNet and CIFAR-10 datasets. Included new references to support dataset and performance analysis, and updated the training configuration to improve GPU performance and resource management.

This simple model, when trained for 30 epochs, achieved a maximum accuracy of 55.8\% at Epoch 29 as shown in Figure \ref{fig:googlenet-simple-accuracy}.

@@

\subsection{Model Evaluation}
Both networks were evaluated using two sets of images. The first is the 1,000 ImageNet images set aside prior to model training. The second set is sourced from the CIFAR-10 dataset. The CIFAR-10 dataset contains 1,000 32x32 RGB images.

\subsubsection{Performance On Unseen Imagenet Images}

\subsubsection{Performance On CIFAR-10 Images}

@@

One of the challenges we encountered was the high computational demand of training, event on the subset of ImageNet images we used. Although GoogLeNet is more efficient than many of its contemporaries, training still required GPU resources. We used data augmentation techniques, such as random cropping, random horizontal flipping, and random zoom to avoid overfitting. We also needed to reduce the learning rate to 0.0001 and reduce batch size to 16 so as not to overwhelm the GPU. The training performance is summarized in Table \ref{tab:training_times}

\begin{table}[ht]
    \centering
    \begin{tabular}{llll}
    \hline
    \textbf{Model} & \textbf{Batch size} & \textbf{Epochs} & \textbf{Training time (minutes)} \\  \hline
    Simple & 16 & 30 & ?? \\ \hline
    Complex & 16 & 30 & 69 \\ \hline
    \end{tabular}
    \caption{Training times}
    \label{tab:training_times}
\end{table}

>>>>

This simple model, when trained for 30 epochs, achieved a maximum accuracy of 57.2\% at Epoch 23 as shown in Figure \ref{fig:googlenet-simple-accuracy}.

@@

\subsection{Model Evaluation}
Both networks were evaluated using two sets of images. The first is the 1,000 ImageNet images set aside prior to model training. The second set is sourced from the CIFAR-10 dataset\cite{kim_cifar10_images}. The CIFAR-10 dataset contains 1,000 32x32 RGB images.

\subsubsection{Performance On Unseen Imagenet Images}
100 images from each class was set aside in order to evaluate the performance of the two models on unseen images. The accuracy of the two models is shown in \ref{tab:perf-unseen-imagenet}.

\begin{table}[ht]
    \centering
    \begin{tabular}{ll}
    \hline
    \textbf{Model} & \textbf{Accuracy} \\ \hline
    Simple & 58.1\% \\ \hline
    GoogLeNet Reproduction & ??? \\ \hline
    \end{tabular}
    \caption{Models' performance on unseen ImageNet images}
    \label{tab:perf-unseen-imagenet}
\end{table}

The simpler model's accuracy of 58.1\% on the test set is slightly better than the training accuracy of 57.2\%. This indicates that the model generalizes well and did not merely memorize the training images. In machine learning, when a model performs well on unseen data compared to the training data, it suggests that the model has learned useful patterns that extend beyond the specific examples in the training set.

Furthermore, the relatively small difference in training accuracy and evaluation accuracy indicates that the model has managed to avoid overfitting. Overfitting typically results in high training accuracy but significantly lower evaluation accuracy. The fact that the model's test accuracy is slightly higher than its training accuracy can be attributed to augmentation done on the training set but not the evaluation set.

On the other hand, the 58.1\% accuracy also indicates that there is room for improvement, suggesting that the model might benefit from more complexity or further tuning.

\subsubsection{Performance On CIFAR-10 Images}
The CIFAR-10 dataset consists of 1,000 32x32 RGB images (100 images per class). The accuracy of the two models against the unseen CIFAR-10 images is shown in \ref{tab:perf-unseen-imagenet}.

\begin{table}[ht]
    \centering
    \begin{tabular}{ll}
    \hline
    \textbf{Model} & \textbf{Accuracy} \\ \hline
    Simple & 21.4\% \\ \hline
    GoogLeNet Reproduction & ??? \\ \hline
    \end{tabular}
    \caption{Models' performance on unseen CIFAR-10 images}
    \label{tab:perf-unseen-imagenet}
\end{table}

The low accuracy of 21.4\% achieved by the simple model could be for several reasons. First, the models were trained on images having a relatively high resolution compared to CIFAR-10's 32x32 images. When models are trained on larger images, the models learn to identify fine-grained details which can become indistinguishable when downscaled to much smaller dimensions~\cite{simonyan2015vgg}.

Additionally, the convolutional filters in the models are likely too large for the small CIFAR-10 images, causing the network to miss out on important features. In a 32x32 image, for instance, using large filter sizes or pooling layers can result in excessive downsampling, leading to a significant loss of spatial information, which ultimately hampers the model's ability to classify the images accurately.

Finally, CIFAR-10, like ImageNet, contains complex image classes, which are often difficult to distinguish at such a low resolution. The limited information provided by 32x32 images presents additional challenges for models trained on high-resolution images, as they may rely on more detailed textures and edges, which are not as pronounced in low-resolution images~\cite{krizhevsky2012imagenet}.

@@

One of the challenges we encountered was the high computational demand of training, event on the subset of ImageNet images we used. Although GoogLeNet is more efficient than many of its contemporaries, training still required GPU resources. We used data augmentation techniques, such as random cropping, random horizontal flipping, and random zoom to avoid overfitting. We also needed to reduce the learning rate to 0.0001, reduced batch size to 16, and enabled memory growth\cite{tensorflow_memory_growth} so as not to overwhelm the GPU. Prefetching was also implemented to improve performance\cite{tensorflow_data_performance}. The training performance is summarized in Table \ref{tab:training_times}

\begin{table}[ht]
    \centering
    \begin{tabular}{llll}
    \hline
    \textbf{Model} & \textbf{Batch size} & \textbf{Epochs} & \textbf{Training time (minutes)} \\  \hline
    Simple & 16 & 30 & 73 \\ \hline
    Complex & 16 & 30 & 69 \\ \hline
    \end{tabular}
    \caption{Training times}
    \label{tab:training_times}
\end{table}
